Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-17 paper.tex
fixed typos and added references
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

An efficient way to synthesize reliable ECPSs is Counterexample Guided Inductive Synthesis (CEGIS)~\cite{David15}. Its key idea is the definition (by a user) of a set of safe states, {\it i.e.}, the specification of $\Phi$, as well as a generic template for a control system that must satisfy such a specification. Then, a CEGIS engine compute values for the unknown symbols of the chosen template, which hold $\Phi$~\cite{RienerKFB16}. Abate~{\it et al.}~\cite{Abate17,abatecav2017} presented a method for synthesizing stable controllers that are suitable to continuous plants given as transfer functions~\cite{Abate17} and state-space representations~\cite{abatecav2017}, which exploits bit-accurate verification of software implemented in digital microcontrollers~\cite{Bessa16,Bessa17,dsv_spin2015}, and the resulting systems must ensure non-fragile stability~\cite{Abate17} and safety~\cite{abatecav2017}. Ravanbakhsh and Sankaranarayanan~\cite{Ravanbakhsh15,Ravanbakhsh16} also employed CEGIS based on the Lyapunov's function to ensure the robust reach-while-stay property ({\it i.e.}, a safety specification)~\cite{Ravanbakhsh16} and non-zeno behavior~\cite{Ravanbakhsh15}. CEGIS was also employed to synthesize model predictive controllers for a wide varieties of applications, {\it e.g.} heating ventilation and air conditioning systems, autonomous vehicles control, and aircraft electric power system~\cite{Ghosh05,Rahman13}.

CEGIS is an important, but not the unique, example of symbolic control synthesis for ECPSs. The main advantage of using symbolic synthesis techniques ({\it e.g.}, SMT- and SAT-based) is the possibility of encoding (via logic formulae) reachability/safety specifications on original concrete systems. Indeed, there are many studies~\cite{Rungger13,AydinGol14,Holub16,Tabuada08,Zamani17,Zamani14,Zamani13,Zamani12,Alkhatib17,Lesser15,Girard13} on symbolic control synthesis for ECPS, available in literature.

A common procedure for controller synthesis for ECPS is based on finite-state approximations of infinite-states systems, {\it i.e.}, the HA. Such an approach allows the fully automated synthesis of ECPS control systems that ensure achievement of complex specifications; however, the main weakness of this approach is that it often produces complex controllers with high implementation cost. In order to avoid that problem, refined controllers have been proposed, which aim to provide some invariant properties for close-loop systems, {\it e.g.}: safety~\cite{Dallal17,Dallal13,Girard13}, reachability~\cite{Alkhatib17,Habets06}, stability~\cite{Zamani12,Tabuada08}, and safety/reachability properties, considering quantization effects~\cite{Reissig17}.

>>>>

An possible approach to synthesize reliable ECPSs is Counterexample Guided Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. Its key idea is the definition (by a user) of a set of safe states, {\it i.e.}, the specification of $\Phi$, as well as a generic template for a control system that must satisfy such a specification. Then, a CEGIS engine computes values for the unknown symbols of the chosen template, which hold $\Phi$~\cite{RienerKFB16}. Abate~{\it et al.}~\cite{Abate17,abatecav2017} presented a method for synthesizing stable controllers that are suitable to continuous plants given as transfer functions~\cite{Abate17} and state-space representations~\cite{abatecav2017}, which exploits bit-accurate verification of software implemented in digital microcontrollers~\cite{Bessa16,Bessa17,dsv_spin2015}, and the resulting systems must ensure non-fragile stability~\cite{Abate17} and safety~\cite{abatecav2017}. Ravanbakhsh and Sankaranarayanan~\cite{Ravanbakhsh15,Ravanbakhsh16} also employed CEGIS based on the Lyapunov's function to ensure the robust reach-while-stay property ({\it i.e.}, a safety specification)~\cite{Ravanbakhsh16} and non-zeno behavior~\cite{Ravanbakhsh15}. CEGIS was also employed to synthesize model predictive controllers for a wide varieties of applications, {\it e.g.}, heating ventilation and air conditioning systems, autonomous vehicles control, and aircraft electric power system~\cite{Ghosh05,Rahman13}.

CEGIS is an important, but not the unique, example of symbolic control synthesis for ECPSs. The main advantage of using symbolic synthesis techniques ({\it e.g.}, SMT- and SAT-based) is the possibility of encoding (via logic formulae) reachability/safety specifications on original concrete systems. Indeed, there are many studies~\cite{Rungger13,AydinGol14,Holub16,Tabuada08,Zamani17,Zamani14,Zamani13,Zamani12,Alkhatib17,Lesser15,Girard13} on symbolic control synthesis for ECPS, available in the literature.

A common procedure for controller synthesis for ECPS is based on finite-state approximations of infinite-states systems, {\it i.e.}, the HA. Such an approach allows the fully automated synthesis of ECPS control systems, which ensure complex specifications realization; however, the main weakness of this approach is that it often produces complex controllers with high implementation cost. In order to avoid that problem, refined controllers have been proposed, which aim to provide some invariant properties for close-loop systems, {\it e.g.}, safety~\cite{Dallal17,Dallal13,Girard13}, reachability~\cite{Alkhatib17,Habets06}, stability~\cite{Zamani12,Tabuada08}, and safety/reachability properties, considering quantization effects~\cite{Reissig17}.
